Towards Detecting Stalkerware Through Network Traces

### 2019-03-18 paper/main.tex
Update main.tex
The table

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em 
b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\section{Apps and Signatures}

\end{document}

>>>>

\usepackage{makecell}
\renewcommand\cellalign{tl}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em 
b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\section{Apps and Signatures}
\begin{table*}
\begin{tabular}{p{5cm}p{5cm}p{5cm}}
	\toprule
	App & Signature & Relevant Info \\
	\midrule
	HelloSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net} & Same as TheTruthSpy HTTP \\

	TheTruthSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net\\ User agent has hellospy in it} & Same as HelloSpy HTTP \\

	SpyMyFone & \makecell{HTTP 101 Switching Protocols response\\
	Domain: data-api.spymyfone.com\\SNI my.spymyfone.com.\\
	Domain: ws.spyzie.com\\SNI ws.spyzie.com\\
	Domains: app-api.phonedata.me\\ws.phonedata.me\\
	SNI with unknown domain:\\ app-api.phonedata.me} & Uses WebSocket protocol and HTTP with User agent=aliyun-sdk-android/2.3.0/Dalvik/2.1.0 (Linux; U; Android 7.1.2; Nexus 5X Build/NJH47B \\

	Spyzie & \makecell{The same as SpyMyFone.\\ We are sure that SpyMyPhone\\ talks to spyzie.com} & Same as SpyMyFone \\

	iSpyoo & probably same signatures as HelloSpy and TheTruthSpy given identical websites, but apk is broken & Nonfunctional \\

	mSpy & \makecell{POST to pipe.thd.cc\\
	PUT to a18.dav.mspyonline.com\\
	Domain: apiv4.alter757.info} & HTTPS \\

	SMS Tracker (TheHar) & \makecell{Domain:uploads.spy2mobile.com\\ Domain contains sap4mobile} & spytomobile group (does NOT use HTTPS) \\

	SMS Tracker TM & \makecell{Domain:cust-198-154-111-218.\\corexchange.com \\ SNI:messages02.smstracker.com} & Only tracks text. HTTPS \\

	Find My Friends & Domain:production-finderapps-lb-1188906093.us-east-1.elb.amazonaws.com & HTTPS\\

	Avast Anti-Theft & domain:Antitheft.ns1.ff.avast.com& HTTPS. High packet counts\\

	Family Locator by ZoeMob & SNIs: celulocen.zendesk.com, api.familysafetyproduction.com
	Domains: proxy.vip.pod5.iad1.zdsys.com, www.zoemob.com & same as Life360
	HTTPS \\

	Couple Tracker -Mobile monitor & 162-144-96-67.unifiedlayer.com & HTTPS \\

	Call and Message Tracker -Remote karanth & \makecell{SNI=www.callsmstracker.com
	\\Domain contains onlinehome-server.com} & Similar to Cell Tracker, but uses HTTPS instead of HTTP \\

	Mobile Surveillance and Security
	by Trackview & \makecell{HTTP req:\\ "GET /create\_session HTTP/1.1"\\ User agent:test \\Host:relay.google.com\\
	Domains: relay.l.google.com,\\ stun.l.google.com} & Uses STUN protocol \\

\end{tabular}
\end{table*}

\begin{table*}
\begin{tabular}{p{5cm}p{5cm}p{5cm}}
	\toprule
	App & Signature & Relevant Info \\
	\midrule
	Norton Family parental control & \makecell{domain: spoc-muw1.norton.com,\\spoc-mue1.norton.com\\
	User-Agent: NOF/4.9.2.12/Android/8.1.0\\
	SNI: family.norton.com} & HTTP POST with protobufs, or TLS. \\

	Senior Safety App & \makecell{POST to \\97.logger.mobi/signalr\_v1/<stuff>\\
	97.logger.mobi/auth/token} & requires payment\\

	Invisible Mobile GPS Tracker by
	GPSWOX.COM & \makecell{SNI:dn.gpswox.com\\ Domain:gpswox.\\llcspnavigatio.netdna-cdn.com} & HTTPS \\

	Family GPS Locator by GeoZilla & \makecell{Domain=static.<some-ip>.\\clients.your-server.de\\
	SNI contains geozilla w/ aws domains} & NOT HTTPS (wrong ports), but TLS \\

	Phone Tracker By Number/Phone Tracker Family Locator & http://66.147.232.135:8080/signalr & HTTP \\

	Automatic Call Recorder & \makecell{Domain: http://winner-lb2-\\f918b4c7bf5ab40c.\\elb.us-east-1.amazonaws.com/ }& HTTPS \\

	Find my Kids: Child GPS-watch and phone tracker & server name api.findmykids.org & Talks to yandex.net? Russian something. 
	HTTPS \\

	Live Mobile Number Tracker & \makecell{GET with host=clk.trkmobi.net\\
	SNI track.56txs4.com, no domain\\
	Domain cs156.adn.rhocdn.net\\ with SNI req..startappservice.com,\\
	domain cs1112.wpc.rhocdn.net\\ with SNI info.startappservice.com} & No actual tracking functions. Sets your location to Fawn creek, KS \\

	track my phone pro & Domain:trackmyphones.com & HTTPS from the website, HTTP over TLS from the app \\

	Cell Phone Tracker & Domain:spy2mobile.com & SpyToMobile lookalike \\

	Cell Tracker - Trackme & Domain:Onlinehome-server.com
	SNI:www.callsmstracker.com & Similar to Call and Message tracker. Sends a post to a separate service. \\

	Texting, Chat, Phone Spy by Maxlo & Domain:spy2mobile.com & SpyToMobile lookalike \\
\end{tabular}

\end{table*}
\end{document}
